
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% declaration %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\addcontentsline{toc}{chapter}{Declaration}


\begin{center}
{\LARGE \textbf{Declaration of Originality}}
\end{center}


I hereby declare that the work which is being presented in the thesis entitled \textbf{$<$TITLE OF THESIS$>$} has been solely authored by me. It presents the result of my own independent investigation/research conducted during the time period from $<$Month and year of joining the Ph.D. program$>$ to $•<$Month and year of Ph.D. Thesis submission$>$ under the supervision of $<$Name of the Ph.D. Thesis Supervisor \# 1, Designation, and Affiliation$>$ and $<$Name of the PhD Thesis Supervisor \# 2, Designation, and Affiliation$>$. To the best of my knowledge, it is an original work, both in terms of research content and narrative, and has not been submitted or accepted elsewhere, in part or in full, for the award of any degree, diploma, fellowship, associateship, or similar title of any university or institution. Further, due credit has been attributed to the relevant state-of-the-art and collaborations (if any) with appropriate citations and acknowledgments, in line with established ethical norms and practices. I also declare that any idea/data/fact/source stated in my thesis has not been fabricated/ falsified/ misrepresented. All the principles of academic honesty and integrity have been followed. I fully understand that if the thesis is found to be unoriginal, fabricated, or plagiarized, the Institute reserves the right to withdraw the thesis from its archive and revoke the associated Degree conferred. Additionally, the Institute also reserves the right to appraise all concerned sections of society of the matter for their information and necessary action (if any). If accepted, I hereby consent for my thesis to be available online in the Institute’s Open Access repository, inter-library loan, and the title \& abstract to be made available to outside organizations.\\[1 cm]



Signature\\

Name: \\
Entry Number: \\
Program: PhD/M.Tech/M.Sc. \\
Department: \\
Indian Institute of Technology Ropar \\
Rupnagar, Punjab 140001 \\

Date:


\newpage

